Road Segment Prioritization for Bicycle Infrastructure

### 2021-03-06 README.Rmd
expand -> address limitations of past research

A considerable amount of research has been done to understand what gets people to cycle.
Segregated cycling infrastructure^[*Segregated cycling infrastructure*
refers to road space that is allocated to cyclists only, with physical
separation to protect cyclists from other modes of transport.] has been
shown to increase cycling uptake [@aldred2019impacts; @goodman2014new;
@marques2015infrastructure], with the separation from motorized
vehicles being key [@winters2011motivators]. Revealed preference of
cyclists shows that they are willing to deviate from the most efficient
routes in order to commute on safer roads [@crane2017longitudinal].
However, such deviations are only considered if they do not considerably
increase route circuitry; behaviour studies have found that the
probability of choosing a route decreases in proportion to its length
relative to the shortest route [@broach2011bicycle; @winters2010far].
Another defining feature for cycling infrastructure is how well
connected it is. Cyclists prefer cohesive infrastructure, particularly
when cycling on arterial roads with high levels of motorized traffic
[@stinson2003commuter]. The lack of well-connected cycling
infrastructure is one of the main obstacles to increasing cycling uptake
[@caulfield2012determining]. While direct and cohesive cycling networks
have been shown to positively impact cycling rates, density^[making an
area's bicycle network denser means adding more cycling routes in the
area and thereby giving cyclists more route options] of the cycling
network is also vital [@schoner2014missing].

@@

Our work builds on these *community finding* approaches by proposing a
similar greedy network expansion algorithm for cycle network expansion
within communities. We incorporate community finding methods for study
area partitioning with weighted routing to avoid links that are
stressful to cycle on. In doing so, we propose a methodology that
accounts for motivators and deterrents to cycling. We propose three
sub-methodologies that expand on some of the limitations of previous
studies. These limitations include (a) bias inherent when basing network
design solely on existing cycling demand, (b) proposing routes that may
not correspond to studies on cyclist preference and government policies,
and (3) insufficient consideration of the ethical principles underlying
the analysis. Section \@ref(calculating-potential-cycling-demand)
focuses on calculating potential cycling demand. Section \@ref(routing)
focuses on routing the demand onto the road network while accounting for
cyclist preferences and government priorities. Section
\@ref(road-segment-prioritisation) outlines a methodology for partitioning the
study area based on a community finding algorithm and routed cycling
demand. It then introduces the network expansion algorithms, and compares an approach grounded in
'egalitarianism' to one grounded in 'utilitarianism'.

>>>>

Much research has been done to understand what gets people to cycle.
Segregated cycling infrastructure^[*Segregated cycling infrastructure*
refers to road space that is allocated to cyclists only, with physical
separation to protect cyclists from other modes of transport.] has been
shown to increase cycling uptake [@aldred2019impacts; @goodman2014new;
@marques2015infrastructure], with the separation from motorized
vehicles being key [@winters2011motivators]. Revealed preference of
cyclists shows that they are willing to deviate from the most efficient
routes in order to commute on safer roads [@crane2017longitudinal].
However, such deviations are only considered if they do not considerably
increase route circuitry; behaviour studies have found that the
probability of choosing a route decreases in proportion to its length
relative to the shortest route [@broach2011bicycle; @winters2010far].
Another defining feature for cycling infrastructure is how well
connected it is. Cyclists prefer cohesive infrastructure, particularly
when cycling on arterial roads with high levels of motorized traffic
[@stinson2003commuter]. The lack of well-connected cycling
infrastructure is one of the main obstacles to increasing cycling uptake
[@caulfield2012determining]. While direct and cohesive cycling networks
have been shown to positively impact cycling rates, density^[making an
area's bicycle network denser means adding more cycling routes in the
area and thereby giving cyclists more route options] of the cycling
network is also vital [@schoner2014missing].

@@

Our work builds on these *community finding* approaches by proposing a
similar greedy network expansion algorithm for cycle network expansion
within communities. We incorporate community finding methods for study
area partitioning with weighted routing to avoid links that are
stressful to cycle on. In doing so, we propose a methodology that
accounts for motivators and deterrents to cycling. We propose three
sub-methodologies that address on some of the limitations of previous
studies. These limitations include (a) bias inherent when basing network
design solely on existing cycling demand, (b) proposing routes that may
not correspond to studies on cyclist preference and government policies,
and (3) insufficient consideration of the ethical principles underlying
the analysis. Section \@ref(calculating-potential-cycling-demand)
focuses on calculating potential cycling demand. Section \@ref(routing)
focuses on routing the demand onto the road network while accounting for
cyclist preferences and government priorities. Section
\@ref(road-segment-prioritisation) outlines a methodology for partitioning the
study area based on a community finding algorithm and routed cycling
demand. It then introduces the network expansion algorithms, and compares an approach grounded in
'egalitarianism' to one grounded in 'utilitarianism'.
